Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-08 p2/def-filesystem.tex
Workaround to |D|=1

An essential assumption in our model is that there is only
a \emph{single directory value} ($|\setd|=1$).
The realisation that
this creates a symmetry between directories and empty nodes
and makes it possible to exploit a hidden symmetry in filesystem commands
that allows formulating a correct and complete reconciliation algorithm
is one of the main contributions of this paper.

This assumption does not hinder the applicability of our results.
In fact, commercial designs for synchronizers 
often avoid considering metadata in directories as % TODO expand
as these are generally not understood well by users,
and, if needed, conflict resolution on these settings can be easily automated
\cite{BZ}.

>>>>

An essential assumption in our model is that there is only
a \emph{single directory value} ($|\setd|=1$).
The realisation that
this creates a symmetry between directories and empty nodes
and makes it possible to exploit a hidden symmetry in filesystem commands
that allows formulating a correct and complete reconciliation algorithm
is one of the main contributions of this paper.
In \cref{sec_multidir} we explore the applicability of our model given this assumption:
why applicability may not be affected and ways to relax this restriction.

### 2018-07-08 p2/multidir.tex
Workaround to |D|=1

% TODO

>>>>

We note that commercial designs for synchronizers 
often avoid considering metadata in directories as
as these are generally not understood well by users,
and, if needed, conflict resolution on these settings can be easily automated.
See, for example, the seminal work of Balasubramaniam and Pierce and the Unison synchronizer \cite{BP} or \cite{BZ}.

Despite the above, there can be applications where directory metadata
is considered important.
Synchronizers based on our model can be readily extended to handle them
by duplicating $\setn$. 
Given the input filesystems, we add a special node as an extra child under each original node,
and we encode directory metadata in a file under each directory.
It is easy to see that update detection and conflict resolution can continue as expected,
with the only exception of a potential conflict detected on one of these special nodes.
In these cases the synchronizer may prescribe creating a directory without creating
the special metadata file, which is clearly not possible to do on the target filesystem,
as creating a directory entails specifying its metadata as well.
In these cases, the synchronizer can either fall back to default values and flag the issue
for review later, or if, as suggested above, conflicts on the metadata (e.g. readable, writeable and executable flags)
can be easily automated, then it could form part of the implementation.
